### 2022-08-24 article.tex
EOD

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).
However, upon the find of a new bug, the question is:
does all the research that use that software still 
result in the same conclusions?
A code hosting website usually has a place to report bugs
that offer transparency in the handling of bug reports.

@@

The most reproducible way of submitting the code of an experiment,
is by providing the code with its dependencies installed in a virtual container.
This is close to the golden standard suggested by 
\cite{peng2011reproducible} (see also Figure \ref{fig:peng2011reproducible}),
however, that was before virtualization existed.
Virtualization allows one to provide a standard environment,
that can be used on any other computer.
The best known examples of container software are Docker and Singularity,
where the latter is the only viable option to be able to run
an experiment on a high performance computing (HPC) environment,
such as a computer cluster.

>>>>

There is another problem that authors of academic code face,
which is that they may be contacted with a user 
asking for technical report 
(against which a 'no' is just fine \cite{barnes2010publish})
or -more relevant to the research- sending in a bug report.
One solution for the author is to ignore such emails
and it can be argued that no energy should be wasted on published code
and work on something new instead 
(see \cite{barnes2010publish} for a better way to deal with the problem).
However, upon the find of a new bug, the question is:
does all the research that use that software still 
result in the same conclusions?
To prevent authors chosing to hide bug reports, 
a code hosting website usually has a public place to report bugs,
to increase transparency in the handling of bug reports.

@@

The most reproducible way of submitting the code of an experiment,
is by providing the code with all the (software) dependencies 
it needs installed in a virtual container.
This is close to the golden standard suggested by 
\cite{peng2011reproducible} 
\iffalse
(see also Figure \ref{fig:peng2011reproducible})
\fi
,
however, that article was written before virtualization existed.
Virtualization allows one to provide a standard environment,
that can be used on any other computer.
The best known examples of container software are Docker and Singularity.
Due to access rights, Singularity is the only viable option to run
an experiment on a 
high performance computing (HPC) environment (e.g. a computer cluster).
